Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-22 manuscript/climate_sensitivity_draft.Rmd
references
#128

Many studies have shown that within and across species, large trees tend to be more affected by drought. 
Greater growth reductions for larger trees were first shown on a global scale by @bennett_larger_2015, and subsequent studies have reinforced this finding [*e.g.*, @hacket-pain_consistent_2016; **REF**]. 
It has yet to be resolved which of several potential underlying mechanisms most strongly shape these trends in drought response. 
First, tree height itself may be a primary driver. 
Taller trees face the biophysical challenge of lifting water greater distances against the effects of gravity and friction [@mcdowell_relationships_2011; @mcdowell_darcys_2015; @ryan_hydraulic_2006; @couvreur_water_2018]. 
Vertical gradients in stem and leaf traits--including smaller and thicker leaves (higher leaf mass per area, LMA), greater resistance to hydraulic dysfunction (*i.e.*, more negative water potential at 50% loss of hydraulic conductivity, more negative P50), and lower hydraulic conductivity at greater heights [@couvreur_water_2018; @koike_leaf_2001; @mcdowell_relationships_2011]--enable trees to become tall [@couvreur_water_2018].
Greater stem capacitance (*i.e.*, water storage capacity) of larger trees may also confer resistance to transient droughts (**REF**).
Indeed, tall trees require xylem of greater hydraulic efficiency, such that xylem conduit diameters are wider in the basal portions of taller trees, both within and across species [@olson_plant_2018; @liu_hydraulic_2019], and throughout the conductive systems of angiosperms (*Zak et al. 2010, Olson et al. 2014,2018*). 
Wider xylem conduits plausibly make large trees more vulnerable to embolism during drought [@olson_plant_2018], and traits conducive to efficient water transport may also lead to poor ability to recover from or re-route water around embolisms [@roskilly_conflicting_2019].

>>>>

Many studies have shown that within and across species, large trees tend to be more affected by drought. 
Greater growth reductions for larger trees were first shown on a global scale by @bennett_larger_2015, and subsequent studies have reinforced this finding [*e.g.*, @hacket-pain_consistent_2016]. 
It has yet to be resolved which of several potential underlying mechanisms most strongly shape these trends in drought response. 
First, tree height itself may be a primary driver. 
Taller trees face the biophysical challenge of lifting water greater distances against the effects of gravity and friction [@mcdowell_relationships_2011; @mcdowell_darcys_2015; @ryan_hydraulic_2006; @couvreur_water_2018]. 
Vertical gradients in stem and leaf traits--including smaller and thicker leaves (higher leaf mass per area, LMA), greater resistance to hydraulic dysfunction (*i.e.*, more negative water potential at 50% loss of hydraulic conductivity, more negative P50), and lower hydraulic conductivity at greater heights [@couvreur_water_2018; @koike_leaf_2001; @mcdowell_relationships_2011]--enable trees to become tall [@couvreur_water_2018].
Greater stem capacitance (*i.e.*, water storage capacity) of larger trees may also confer resistance to transient droughts (*Phillips et al. 2003; DOI:10.1093/treephys/23.4.237; Scholz et al. 2011*).
Indeed, tall trees require xylem of greater hydraulic efficiency, such that xylem conduit diameters are wider in the basal portions of taller trees, both within and across species [@olson_plant_2018; @liu_hydraulic_2019], and throughout the conductive systems of angiosperms (*Zak et al. 2010, Olson et al. 2014,2018*). 
Wider xylem conduits plausibly make large trees more vulnerable to embolism during drought [@olson_plant_2018], and traits conducive to efficient water transport may also lead to poor ability to recover from or re-route water around embolisms [@roskilly_conflicting_2019].
